Type-Safe Client-Server Communication in Web Applications

### 2014-02-26 paper.tex
Add reference for STG.

\paragraph{Implementation} As previously mentioned, Haste offloads much of the
heavy lifting of compilation - parsing, type checking, intermediate code
generation and many optimizations - onto GHC, and takes over code generation
after the STG generation step, at the very end of the compilation process.
STG is the last intermediate representation used by the GHC compiler before
the final code generation takes place and has several benefits:

@@

>>>>

\paragraph{Implementation} As previously mentioned, Haste offloads much of the
heavy lifting of compilation - parsing, type checking, intermediate code
generation and many optimizations - onto GHC, and takes over code generation
after the STG generation step, at the very end of the compilation process.
STG\ \cite{stg} is the last intermediate representation used by GHC before
the final code generation takes place and has several benefits for use as
Haste's target language:

@@

\bibitem[Peyton Jones (1992)]{stg}
S. Peyton Jones: Implementing lazy functional languages on stock hardware: the Spineless Tagless G-machine, Journal of Functional Programming, 1992
